HTLSDstack

### 2025-05-14 Code/R/Research/HTLSDstack.Rmd
htlsd methods compare

```{r setup, include=FALSE}
library(Rssa)
library(rTensor)
library(ggplot2)
library(dplyr)
library(tidyr)
library(future.apply)
library(progressr)

@@

```{r}
rrmse <- function(true, pred, k) {
  sqrt(sum((pred - true[k])^2) / length(pred)) * 100 / (0.5 * abs(true[1] - true[2]))
}

@@

# Example 1
A <- c(1, 1)
phi <- c(0, 0)
rate <- c(0, 0)
freq <- c(0.2, 0.205)
L_esprit <- 500
L_htlsd <- 50
L_tens <- 50
D <- 10
groups_esprit <- list(1:2)
groups_htlsd <- list(1:2)
groups_tens <- list(1:2)
r3 <- 2
est_dim <- 1
dt <- 0.1
N <- 1000
true_freq <- freq * dt

@@

```{r}
sd <- snr_to_sd(s, snr = 30)
R <- 100

estims <- replicate(R, compare_htls())
```

>>>>

```{r setup, include=FALSE}
library(svd)
library(Rssa)
library(rTensor)
library(ggplot2)
library(dplyr)
library(tidyr)
library(future.apply)
library(progressr)

@@

```{r}
rrmse <- function(true, pred) {
  c(sqrt(mean((pred[1, ] - true[1])^2)) * 100 / (0.5 * abs(true[1] - true[2])),
    sqrt(mean((pred[2, ] - true[2])^2)) * 100 / (0.5 * abs(true[1] - true[2])))
}

@@

# Example 1
A <- c(1, 1)
phi <- c(0, 0)
rate <- c(0, 0)
freq <- c(0.2, 0.205)
L_esprit <- 500
L_htlsd <- 50
L_tens <- 50
D <- 10
groups_esprit <- list(1:2)
groups_htlsd <- list(1:2)
groups_tens <- list(1:2)
r3 <- 2
est_dim <- 1
dt <- 0.1
N <- 1000

@@

```{r warning=FALSE}
sd <- snr_to_sd(s, snr = 30)
R <- 100
with(plan(multisession), {
  library(svd)
batch_estims <- function(R) {
  p <- progressor(R)
  future_replicate(R, {
    p()
    compare_htls()
  }, simplify = "array", future.seed = 5)
}
estims <- batch_estims(R)
})

freq_estims <- apply(estims[3:4,,], 2:3, function(v) c(min(abs(v)), max(abs(v))) / dt)

esprit_rrmse <- apply(freq_estims, 2, rrmse, true = freq)
```
